---
title: "p8105_hw1_jl7033"
author: "Joe LaRocca"
date: "2024-09-19"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

```{r}

data("penguins", package = "palmerpenguins")

penguins

```

The data include the species of penguin, the island the penguin comes from, the penguins' bill length, bill depth, and flipper length (all measured in mm), their body mass (measured in g), their sex (male or female) and the year in which the data point was taken (from 2007 to 2009, inclusive).

The dataset has `r nrow(penguins)` rows, meaning that there are `r nrow(penguins)` penguins in the dataset. It has `r ncol(penguins)` columns, so there are a total of `r ncol(penguins)` variables being measured.

The mean flipper length is about `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm, not including penguins for which the flipper length value is missing.

```{r}

flipper_bill_plot = ggplot(data = penguins, 
       aes(x = bill_length_mm, 
           y = flipper_length_mm,
           col = species)) + 
  geom_point() + 
  labs(title = "Plot of Flipper Length vs. Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")

flipper_bill_plot

ggsave(filename = "flipper_bill_plot.png",
  plot = flipper_bill_plot)

```


