---
title: "P8105 - Homework 1"
author: "Joe LaRocca"
date: "September 19, 2024"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Problem 1

##### Upload the Palmer Penguins Data

```{r}

data("penguins", package = "palmerpenguins")

```

The data include the species of penguin, the island the penguin comes from, the penguins' bill length, bill depth, and flipper length (all measured in mm), their body mass (measured in g), their sex (male or female) and the year in which the data point was taken (from 2007 to 2009, inclusive).

The dataset has `r nrow(penguins)` rows, meaning that there are `r nrow(penguins)` penguins in the dataset. It has `r ncol(penguins)` columns, so there are a total of `r ncol(penguins)` variables being measured.

The mean flipper length is about `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm, not including penguins for which the flipper length value is missing.

##### Create the scatterplot for Flipper Length (y) vs. Bill Length (x)

```{r}

flipper_bill_plot = ggplot(data = penguins, 
       aes(x = bill_length_mm, 
           y = flipper_length_mm,
           col = species)) + 
  geom_point() + 
  labs(title = "Plot of Flipper Length vs. Bill Length",
       x = "Bill Length (mm)",
       y = "Flipper Length (mm)")

flipper_bill_plot

ggsave(filename = "flipper_bill_plot.png",
  plot = flipper_bill_plot)

```

## Problem 2

```{r}

problem_2_df = tibble(
  random_normal = rnorm(10, mean = 0, sd = 1),
  logical = random_normal > 0,
  character = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor = factor(
    c("High", "Medium", "Low", "Low", "Medium", 
      "Medium", "High", "Low", "High", "Low"))
)

problem_2_df

```
##### Take the mean of the standard Normal and Logical column

```{r}

problem_2_df %>% 
  pull(random_normal) %>% 
  mean()

```

```{r}

problem_2_df %>% 
  pull(logical) %>% 
  mean()

```

The means of the `random_normal` and `logical` columns are `r mean(problem_2_df$random_normal)` and `r mean(problem_2_df$logical)` respectively. The `character` and `factor` columns have no defined mean; when I try to take their mean, I get an error message saying that the argument is not numeric or logical.

##### Try converting variables using as.numeric()

```{r, eval = FALSE}

problem_2_df %>% 
  mutate(logical = as.numeric(logical)) %>% 
  mutate(character = as.numeric(character)) %>% 
  mutate(factor = as.numeric(factor))

```
Applying `as.numeric()` to the `logical` variable converts all "TRUE" values to "1" and all "FALSE" values to 0. Applying `as.numeric()` to the `character` variable converts all of the characters into `NA`. Applying `as.numeric()` to the `factor` variable converts the variable into numbers corresponding to the alphabetical order of the factor variable. In my case, all "HIGH" values were converted to "1", all "LOW" values were converted to "2", and all "MEDIUM" values were converted to "3".